 ---
title: "Population Structure"
author: "Yantong Li"
date: "7/24/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
```


## Transform Raw population to Distibution
```{r}
age_range = function(population_dataset){
  Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')
  population_dataset$Age_Range = 0
  for (i in 1:nrow(population_dataset)){
    if (population_dataset[i,]$Age %in% 20:24){
      population_dataset[i,]$Age_Range = Age_Range[1]
    }
    else if (population_dataset[i,]$Age %in% 25:28){
      population_dataset[i,]$Age_Range = Age_Range[2]
    }
    else if (population_dataset[i,]$Age %in% 29:31){
      population_dataset[i,]$Age_Range = Age_Range[3]
    }
    else if (population_dataset[i,]$Age %in% 32:35){
      population_dataset[i,]$Age_Range = Age_Range[4]
    }  
    else if (population_dataset[i,]$Age %in% 36:40){
      population_dataset[i,]$Age_Range = Age_Range[5]
    }
    else if (population_dataset[i,]$Age %in% 41:50){
      population_dataset[i,]$Age_Range = Age_Range[6]
    }
    else{
      population_dataset[i,]$Age_Range = Age_Range[7]
    }
  }
  population_dataset
}

```

```{r}
dimission_rate = function(population_dataset= pop_struc){
  population_dataset_group <- age_range(population_dataset)
  dismission_dataset <- population_dataset_group %>% 
    group_by(Age_Range,Year) %>% 
    summarise(Total_Number = sum(Number),
              Dismission_Number = sum(Dismission))
  
  dim_year=  2015:2018
  dimmision_age_range = c()
  dimmision_year = c()  
  dimm_number = c()
  dimm_last_total_n = c()
  for(y in dim_year){
    for (age in Age_Range){
      dismiss_n = as.numeric(dismission_dataset[which((dismission_dataset$Age_Range == age)
                                                      & (dismission_dataset$Year == y)),4])
      last_total_n = as.numeric(dismission_dataset[which((dismission_dataset$Age_Range == age)
                                                         & (dismission_dataset$Year == y-1)),3])
      dimmision_year = c(dimmision_year,y)
      dimmision_age_range = c(dimmision_age_range,age)
      dimm_number=  c(dimm_number,dismiss_n)
      dimm_last_total_n = c(dimm_last_total_n,last_total_n)
      
    }
  }
  dimm_table = as.data.frame(dimmision_year)
  dimm_table$Age_range = dimmision_age_range
  dimm_table$dimmision_number = dimm_number
  dimm_table$last_total_num = dimm_last_total_n
  last_total_number = dimm_table %>% 
    group_by(dimmision_year) %>% 
    summarise(Last_Total_Num = sum(last_total_num)) %>% 
    select(Last_Total_Num)
  dimm_table$dimmision_rate = 0
  for(i in 1:nrow(dimm_table)){
    y = dimm_table$dimmision_year[i]
    rate = dimm_table$dimmision_number[i]/last_total_number$Last_Total_Num[y-2014]
    dimm_table$dimmision_rate[i] = rate
  }
  dimm_table
}

```



```{r}
library(dplyr)
Distribution = function(population_dataset,sub_Year){
  population_dataset_sub = population_dataset[which(population_dataset$Year == sub_Year),]
  population_dataset_group <- age_range(population_dataset_sub)
  dist_dataset <- population_dataset_group %>% 
    group_by(Age_Range) %>%
    summarise(Total_Number = sum(Number),
              Recruitment_Number = sum(Recruitment)
    )   
  
  
  dist_dataset$Dismission_Number = dimm_table[dimm_table$dimmision_year==sub_Year,]$dimmision_number
  dist_dataset$Dismission_Ratio = dimm_table[dimm_table$dimmision_year==sub_Year,]$dimmision_rate
  
  dist_dataset = subset(dist_dataset,select = c(1,2,4,5,3))
  
  # boundary number
  Boundary_Age = c(24,28,31,35,40,50,60)
  Boundary_Age_Number = c()
  for (i in Boundary_Age){
    age_num = population_dataset_sub[which(population_dataset_sub$Age == i),]$Number
    Boundary_Age_Number = c(Boundary_Age_Number,age_num)
  }
  Boundary_Age_Ratio <- Boundary_Age_Number/dist_dataset$Total_Number
  
  total_recruitment = sum(dist_dataset$Recruitment_Number)
  Recruitment_Ratio = dist_dataset$Recruitment_Number/total_recruitment  # ratio for each age range
  dist_dataset = cbind(dist_dataset,Recruitment_Ratio,Boundary_Age,Boundary_Age_Number,Boundary_Age_Ratio)
  
  dist_dataset
}
```




## Transition Matrix from Preview Year to Next Year. (For example, from 2018 to 2019)

```{r}
Transition <- function(Distribution_dataset,sub_year){
  
  Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')
  N_20_24 = rep(0,7)
  N_25_28 = rep(0,7)
  N_29_31 = rep(0,7)
  N_32_35 = rep(0,7)
  N_36_40 = rep(0,7)
  N_41_50 = rep(0,7)
  N_51_60 = rep(0,7)
  Recruitment = Distribution_dataset$Recruitment_Ratio
  Dismission = Distribution_dataset$Dismission_Ratio
  Retirement = c(0,0,0,0,0,0,retire_rate[sub_year-2015])
  
  
  N_25_28[1] = Distribution_dataset$Boundary_Age_Ratio[1]
  N_29_31[2] = Distribution_dataset$Boundary_Age_Ratio[2]
  N_32_35[3] = Distribution_dataset$Boundary_Age_Ratio[3]
  N_36_40[4] = Distribution_dataset$Boundary_Age_Ratio[4]
  N_41_50[5] = Distribution_dataset$Boundary_Age_Ratio[5]
  N_51_60[6] = Distribution_dataset$Boundary_Age_Ratio[6]
  
  Tran_Mtx = cbind(N_20_24,N_25_28,N_29_31,N_32_35,N_36_40,N_41_50,N_51_60,Dismission,Retirement,Recruitment)
  
  for (i in 1:7){
    for (j in 1:7){
      if (i == j){
        if (i < 7){
          Tran_Mtx[i,j] = 1 - Tran_Mtx[i,i+1] - Tran_Mtx[i,8]
        }else{
          Tran_Mtx[i,j] = 1 - Tran_Mtx[i,8] - Tran_Mtx[i,9]
        }
      }
    }
  }
  rownames(Tran_Mtx) <- c('P_20_24','P_25_28','P_29_31','P_32_35','P_36_40','P_41_50','P_51_60')
  as.data.frame(Tran_Mtx)
}
```


```{r}

pre_recruit <- function(pred_year){
  # Predicting by mean
  
  p_total_recruit = predict(lm_total_recruit,data.frame(Year = pred_year))*0.7
  p_20_24_recruit = prob_20_24_recruit*p_total_recruit*1.3
  p_25_28_recruit = prob_25_28_recruit*p_total_recruit*1.3
  p_29_31_recruit = prob_29_31_recruit*p_total_recruit*1.3
  p_32_35_recruit = prob_32_35_recruit*p_total_recruit*1.1
  p_36_40_recruit = prob_36_40_recruit*p_total_recruit*0.5
  p_41_50_recruit = prob_41_50_recruit*p_total_recruit*0.5
  p_51_60_recruit = prob_51_60_recruit*p_total_recruit*0.5
  
  p_recruit_number = c(p_20_24_recruit,p_25_28_recruit,p_29_31_recruit,p_32_35_recruit,
                       p_36_40_recruit,p_41_50_recruit,p_51_60_recruit)
  pre_recruitment = as.data.frame(p_recruit_number)
  rownames(pre_recruitment) = Age_Range
  pre_recruitment
}

```

```{r}
pre_dismission <- function(dist_list){
  
  # Predicting by average
  Total_Number_dim = sum(dist_list[[year_number]]$Total_Number)
  
  p_20_24_dism = (mean(Dismission_Ratio_20_24))*Total_Number_dim
  p_25_28_dism = (mean(Dismission_Ratio_25_28)-0.005)*Total_Number_dim
  p_29_31_dism = (mean(Dismission_Ratio_29_31)-0.005)*Total_Number_dim
  p_32_35_dism = (mean(Dismission_Ratio_32_35))*Total_Number_dim
  p_36_40_dism = (mean(Dismission_Ratio_36_40)+0.05)*Total_Number_dim
  p_41_50_dism = (mean(Dismission_Ratio_41_50)+0.05)*Total_Number_dim
  p_51_60_dism = (mean(Dismission_Ratio_51_60)+0.02)*Total_Number_dim
  
  p_dismission_number = c(p_20_24_dism,p_25_28_dism,p_29_31_dism,p_32_35_dism,p_36_40_dism,p_41_50_dism,p_51_60_dism)
  pre_dismission = as.data.frame(p_dismission_number)
  rownames(pre_dismission) = Age_Range
  pre_dismission
}
```



```{r}
pre_retirement <- function(Tran_list){
  
  
  Total_Number_re = dist_list[[year_number]]$Total_Number[7]
  p_retirement_Ratio_51_60 = predict(lm_Retirement_Ratio_51_60,data.frame(Year = pred_year))*Total_Number_re
  p_retirement_number = c(0,0,0,0,0,0,p_retirement_Ratio_51_60)
  pre_retirement = as.data.frame(p_retirement_number)
  rownames(pre_retirement) = Age_Range
  pre_retirement
}

```


### 5. Predict Boundary Number
```{r}
# predict new population 
# new population = internal transition + new recruitment

#the first bound table


bound_table = function(population_dataset){
  population_dataset_group = age_range(population_dataset)
  Bound_Table = select(population_dataset_group[which(population_dataset_group$Year==pred_year-1),],c(2,6,3,4))
  Bound_Table
}


recuit_cal = function(sub_dataset){
  avg_recruit = c()
  avg_total_recruit = sum(sub_dataset)/nrow(sub_dataset)
  for (i in 1:ncol(sub_dataset)){
    avg_recruit = c(avg_recruit,mean(sub_dataset[,i])/avg_total_recruit)
  }
  avg_recruit
}

```


```{r}


##### 1. internal transition


stay_prob = function(Tran){
  Stay_Prob = c()
  for(age in 20:60){
    if(age %in% 20:24 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[1])}
    else if(age %in% 25:28 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[2])}
    else if(age %in% 29:31 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[3])}
    else if(age %in% 32:35 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[4])}
    else if(age %in% 36:40 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[5])}
    else if(age %in% 41:50 ){Stay_Prob = c(Stay_Prob,1-Tran$Dismission[6])}
    else if(age %in% 51:60 ){
      if (age ==60){
        Stay_Prob = c(Stay_Prob,1-Tran$Dismission[7]-Tran$Retirement[7])
      }else{
        Stay_Prob = c(Stay_Prob,1-Tran$Dismission[7])
      }
    }
  }
  Stay_Prob
}


internal_tranistion = function(Bound_Table,Tran){
  Stay_Prob = stay_prob(Tran)
  
  in_tran = c(0)
  for (i in 1:(nrow(Bound_Table)-1)){
    in_tran = c(in_tran,Bound_Table[i,3]*Stay_Prob[i+1])
  }
  in_tran
}
  
##### 2.new recruitment


new_rec = function(Bound_Table){
  rec_group = Bound_Table %>% 
    group_by(Age_Range) %>% 
    summarise(Total_Recru = sum(Recruitment)) 
  
  New_rec_total = c()
  for(i in 1:nrow(Bound_Table)){
    age = i+19
    if(age %in% 20:24 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[1]/pre_recruitment[1,])}
    else if(age %in% 25:28 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[2]/pre_recruitment[2,])}
    else if(age %in% 29:31 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[3]/pre_recruitment[3,])}
    else if(age %in% 32:35 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[4]/pre_recruitment[4,])}
    else if(age %in% 36:40 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[5]/pre_recruitment[5,])}
    else if(age %in% 41:50 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[6]/pre_recruitment[6,])}
    else if(age %in% 51:60 ){New_rec_total = c(New_rec_total,rec_group$Total_Recru[7]/pre_recruitment[7,])}
  }
  New_rec = Bound_Table$Recruitment/New_rec_total
  New_rec
}



##### 3. New Bound Table
new_Bound_Table = function(Bound_Table){
  Old_Bound_Table = Bound_Table
  Old_Bound_Table$Number = New_rec + in_tran
  Old_Bound_Table$Recruitment = New_rec
  Old_Bound_Table
}

```











## main

### Obtain Dataset
```{r}
pop_struc = read.csv("pop_struc.csv")
pop_struc = pop_struc[,1:5]
#View(pop_struc)
colnames(pop_struc) <- c("Year","Age","Number","Recruitment","Dismission")
Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')
```

calculate dimmission rate
```{r}
dimm_table = dimission_rate(pop_struc)
```



calculate Retirement rate
```{r}
Retire_col = c()
for (i in 2015:2018){
  Retire_col = c(Retire_col,pop_struc[which((pop_struc$Year == i)&(pop_struc$Age == 60) ),]$Number)
}

pop_struc_group = age_range(pop_struc)

retire_table <- pop_struc_group %>% 
    group_by(Age_Range,Year) %>%
    summarise(Total_Number = sum(Number),
              Recruitment_Number = sum(Recruitment)
              )  

retire_rate = Retire_col/retire_table[which(retire_table$Age_Range == '51-60'),]$Total_Number[1:4]
```


```{r}
dist_2015 <- Distribution(pop_struc,2015)
dist_2016 <- Distribution(pop_struc,2016)
dist_2017 <- Distribution(pop_struc,2017)
dist_2018 <- Distribution(pop_struc,2018)
```



```{r}
Tran_Mtx_2015 <- Transition(dist_2015,2016)
Tran_Mtx_2016 <- Transition(dist_2016,2017)
Tran_Mtx_2017 <- Transition(dist_2017,2018)
Tran_Mtx_2018 <- Transition(dist_2018,2019)
```


```{r}
dist_list = list(dist_2015,dist_2016,dist_2017,dist_2018)
Tran_list = list(Tran_Mtx_2015,Tran_Mtx_2016,Tran_Mtx_2017,Tran_Mtx_2018)
year_number = length(dist_list)
Tran =Tran_list[[year_number]]
Dist = dist_list[[year_number]]
```



### Prediction
#### 1. Predict recruitment number for next year
```{r}
pred_year = 2019

Total_Recruit_Numbers <- c()
Recruit_ratio_20_24 <- c()
Recruit_ratio_25_28 <- c()
Recruit_ratio_29_31 <- c()
Recruit_ratio_32_35 <- c()
Recruit_ratio_36_40 <- c()
Recruit_ratio_41_50 <- c()
Recruit_ratio_51_60 <- c() 
for (i in 3:0){
  total = sum(dist_list[[year_number-i]]$Recruitment_Number)
  Total_Recruit_Numbers = c(Total_Recruit_Numbers,total)
  Recruit_ratio_20_24 = c(Recruit_ratio_20_24,Tran_list[[year_number-i]]$Recruitment[1])
  Recruit_ratio_25_28 = c(Recruit_ratio_25_28,Tran_list[[year_number-i]]$Recruitment[2])
  Recruit_ratio_29_31 = c(Recruit_ratio_29_31,Tran_list[[year_number-i]]$Recruitment[3])
  Recruit_ratio_32_35 = c(Recruit_ratio_32_35,Tran_list[[year_number-i]]$Recruitment[4])
  Recruit_ratio_36_40 = c(Recruit_ratio_36_40,Tran_list[[year_number-i]]$Recruitment[5])
  Recruit_ratio_41_50 = c(Recruit_ratio_41_50,Tran_list[[year_number-i]]$Recruitment[6])
  Recruit_ratio_51_60 = c(Recruit_ratio_51_60,Tran_list[[year_number-i]]$Recruitment[7])
}

Year = 2016:2018

lm_total_recruit = lm(Total_Recruit_Numbers[2:4]~Year)
prob_20_24_recruit = mean(Recruit_ratio_20_24)
prob_25_28_recruit = mean(Recruit_ratio_25_28)
prob_29_31_recruit = mean(Recruit_ratio_29_31)
prob_32_35_recruit = mean(Recruit_ratio_32_35)
prob_36_40_recruit = mean(Recruit_ratio_36_40)
prob_41_50_recruit = mean(Recruit_ratio_41_50)
prob_51_60_recruit = mean(Recruit_ratio_51_60)


```


```{r}
pre_recruitment = pre_recruit(pred_year)
```



#### 2. Predict Dimission Number for next year
```{r}

Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')
year_number = length(dist_list)
Dismission_Ratio_20_24 <- c()
Dismission_Ratio_25_28 <- c()
Dismission_Ratio_29_31 <- c()
Dismission_Ratio_32_35 <- c()
Dismission_Ratio_36_40 <- c()
Dismission_Ratio_41_50 <- c()
Dismission_Ratio_51_60 <- c()
for (i in 3:0){
  Dismission_Ratio_20_24 = c(Dismission_Ratio_20_24,Tran_list[[year_number-i]]$Dismission[1])
  Dismission_Ratio_25_28 = c(Dismission_Ratio_25_28,Tran_list[[year_number-i]]$Dismission[2])
  Dismission_Ratio_29_31 = c(Dismission_Ratio_29_31,Tran_list[[year_number-i]]$Dismission[3])
  Dismission_Ratio_32_35 = c(Dismission_Ratio_32_35,Tran_list[[year_number-i]]$Dismission[4])
  Dismission_Ratio_36_40 = c(Dismission_Ratio_36_40,Tran_list[[year_number-i]]$Dismission[5])
  Dismission_Ratio_41_50 = c(Dismission_Ratio_41_50,Tran_list[[year_number-i]]$Dismission[6])
  Dismission_Ratio_51_60 = c(Dismission_Ratio_51_60,Tran_list[[year_number-i]]$Dismission[7])
  
}


```

```{r}
pre_dismission_ = pre_dismission(dist_list) # predict dismissing number for next year in 7 groups
```



#### 3. Predict Retirement Number for next year
```{r}
Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')
Retirement_Ratio_51_60 <- c()
for (i in 3:0){
  Retirement_Ratio_51_60 = c(Retirement_Ratio_51_60,Tran_list[[year_number-i]]$Retirement[7])
}
Year = 2015:2018
lm_Retirement_Ratio_51_60 =  lm(Retirement_Ratio_51_60~Year)
```

```{r}
pre_retirement_ = pre_retirement(Tran_list)
```



```{r}
Bound_Table = bound_table(pop_struc)
in_tran = internal_tranistion(Bound_Table,Tran)
New_rec = new_rec(Bound_Table)
Old_Bound_Table = Bound_Table
Bound_Table = new_Bound_Table(Bound_Table)
```



Compose to the next distribution table with the predictive info
```{r}
Age_Range = c('20-24','25-28','29-31','32-35','36-40','41-50','51-60')

Total_Numbers <- Bound_Table %>% 
  group_by(Age_Range) %>% 
  summarise(total = sum(Number)) %>% 
  select(c(total))
Old_Total_Number <- Old_Bound_Table %>% 
  group_by(Age_Range) %>% 
  summarise(total = sum(Number)) %>% 
  select(c(total))

Dismission_Number = pre_dismission_
Dismission_Ratio = Dismission_Number/sum(Old_Bound_Table$Number)
Recruitment_Number = pre_recruitment
Recruitment_Ratio = Recruitment_Number/sum(pre_recruitment)
Boundary_Age = c(24,28,31,35,40,50,60)
Boundary_Age_Number = Bound_Table[Boundary_Age-19,]$Number
Boundary_Age_Ratio = Boundary_Age_Number/Total_Numbers
Last_Dist = Dist
Next_Dist = cbind(Age_Range,Total_Numbers,Dismission_Number,Dismission_Ratio,Recruitment_Number,Recruitment_Ratio,
                   Boundary_Age,Boundary_Age_Number, Boundary_Age_Ratio)
colnames(Next_Dist) <- colnames(Last_Dist) 

```

```{r}

for (pred_year in 2020:2038){
  
  retire_rate_new = as.numeric( Bound_Table[which(Bound_Table$Age == 60),]$Number/Old_Total_Number[7,])
  retire_rate = c(retire_rate,retire_rate_new)
  
  Next_Tran = Transition(Next_Dist,pred_year)
  
  dist_list[[pred_year-2014]] = Next_Dist
  Tran_list[[pred_year-2014]] = Next_Tran
  year_number = length(dist_list)
  Tran =Next_Tran
  Dist = Next_Dist
  
  ### Prediction
  #### 1. Predict recruitment number for next year
  pre_recruitment = pre_recruit(pred_year)
  
  
  #### 2. Predict Dimission Number for next year
  pre_dismission_ = pre_dismission(dist_list) # predict dismissing number for next year in 7 groups
  
  
  #### 3. Predict Retirement Number for next year
  pre_retirement_ = pre_retirement(Tran_list)
  
  
  #### 4. Predict Bound Table
  in_tran = internal_tranistion(Bound_Table,Tran)
  New_rec = new_rec(Bound_Table)
  Old_Bound_Table = Bound_Table
  Bound_Table = new_Bound_Table(Bound_Table)
  
  
  ### Compose to the next distribution table with the predictive info
  Total_Numbers <- Bound_Table %>% 
    group_by(Age_Range) %>% 
    summarise(total = sum(Number)) %>% 
    select(c(total))
  Old_Total_Number <- Old_Bound_Table %>% 
    group_by(Age_Range) %>% 
    summarise(total = sum(Number)) %>% 
    select(c(total))
  
  Dismission_Number = pre_dismission_
  Dismission_Ratio = Dismission_Number/sum(Old_Bound_Table$Number)
  Recruitment_Number = pre_recruitment
  Recruitment_Ratio = Recruitment_Number/sum(pre_recruitment)
  Boundary_Age = c(24,28,31,35,40,50,60)
  Boundary_Age_Number = Bound_Table[Boundary_Age-19,]$Number
  Boundary_Age_Ratio = Boundary_Age_Number/Total_Numbers
  Last_Dist = Dist
  Next_Dist = cbind(Age_Range,Total_Numbers,Dismission_Number,Dismission_Ratio,Recruitment_Number,Recruitment_Ratio,
                    Boundary_Age,Boundary_Age_Number, Boundary_Age_Ratio)
  colnames(Next_Dist) <- colnames(Last_Dist) 

}
dist_list[[pred_year-2013]] = Next_Dist

```



```{r}
library(ggplot2)
```

```{r}
population = data.frame()
for (dist_index in 1:length(dist_list)){
  dist = dist_list[[dist_index]]
  population = rbind(population,dist$Total_Number)
}
colnames(population) = Age_Range
rownames(population) = 2015:2038

write.csv(population,"population.csv")

```





